\textsf{Are large language models superhuman chemists?}

### 2024-03-28 src/tex/appendix.tex
update authors
include tables of dataset sizes

>>>>

\subsection{Leaderboard}
Our leaderboard is based on the tool chain developed for matbench.\autocite{dunn2020benchmarking} 
Briefly, the \chembench pipeline produces standardized files in \texttt{json} format that contributors can add via pull requests to the \chembench repository.
The Markdown tables and interactive plots are then automatically generated and updated on the \chembench website.

### 2024-03-28 src/tex/authors.tex
update authors
adrian feedback
include tables of dataset sizes

% Question answerers
\credit{Mehrdad Asgari}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Juliane Eberhardt}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Amir Elahi}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Christina Glaubitz}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Maximilian Greiner}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Caroline T. Holick}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Tim Hoffmann}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Lea~C.~Klepsch}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Yannik Köster}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Fabian Alexander Kreth}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Jakob~Meyer}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Jan Matthias Peschel}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Michael Ringleb}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Nicole Roesner}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Johanna Schreiber}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Ulrich~S.~Schubert}{0,0,0,1,0,0,0,0,0,0,0,0,0,1}
\credit{Leanne M. Stafast}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Dinga Wonanke}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}

@@

\author[5]{Mehrdad~Asgari~\orcidlink{0000-0002-5427-1610}}
\author[6]{Juliane~Eberhardt~\orcidlink{0009-0000-3991-0704}}
\author[7]{Amir~Elahi}
\author[]{Christina~Glaubitz~\orcidlink{0000-0003-3412-0548}}
\author[1]{Maximilian~Greiner}
\author[1]{Caroline~T.~Holick\orcidlink{0009-0000-1724-2725}}
\author[1]{Tim~Hoffmann~\orcidlink{0009-0004-0230-6115}}
\author[1]{Lea~C.~Klepsch~\orcidlink{0009-0009-3849-1670}}
\author[1]{Yannik~Köster~\orcidlink{0000-0002-9125-3067}}
\author[8, 9]{Fabian~Alexander~Kreth~\orcidlink{0000-0002-5968-8706}}
\author[1]{Jakob~Meyer}
\author[1]{Jan~Matthias~Peschel~\orcidlink{0009-0002-4787-2757}}
\author[1]{Michael~Ringleb~\orcidlink{0000-0002-7320-8529}}
\author[1, 10]{Nicole~Roesner~\orcidlink{0000-0002-5133-775X}}

\author[1, 10]{Johanna Schreiber~\orcidlink{0009-0000-0991-8967}}
\author[1,8,10, 11]{Ulrich~S.~Schubert~\orcidlink{0000-0003-4978-4670}}
\author[1]{Leanne~M.~Stafast}
\author[10]{Dinga~Wonanke~\orcidlink{0000-0002-9066-2715}}

% Senior authors
\author[12,13]{Michael Pieler~\orcidlink{0000-0001-9186-7045}}
\author[3,4]{Philippe~Schwaller~\orcidlink{0000-0003-3046-6576}}
\author[1,8,10, 11, \Letter]{Kevin~Maik~Jablonka~\orcidlink{0000-0003-4894-4660}}

\affil[1]{Laboratory of Organic and Macromolecular Chemistry (IOMC), Friedrich Schiller University Jena, Humboldtstrasse 10, 07743 Jena, Germany}
\affil[8]{Center for Energy and Environmental Chemistry Jena (CEEC Jena), Friedrich Schiller University Jena, Philosophenweg 7a, 07743 Jena, Germany}
\affil[11]{Helmholtz Institute for Polymers in Energy Applications Jena (HIPOLE Jena), Lessingstrasse 12-14, 07743 Jena, Germany}
\affil[10]{Jena Center for Soft Matter (JCSM), Friedrich Schiller University Jena, Philosophenweg 7, 07743 Jena, Germany}

@@

\affil[7]{Laboratory of Molecular Simulation (LSMO), Institut des Sciences et Ing\'{e}nierie Chimiques, Ecole Polytechnique F\'{e}d\'{e}rale de Lausanne (EPFL), Sion, Switzerland}
\affil[10]{Theoretical Chemistry, Technische Universität Dresden, Dresden 01062, Germany}
\affil[12]{OpenBioML.org}
\affil[13]{Stability.AI}
\affil[9]{Institute for Technical Chemistry and Environmental Chemistry (ITUC), Friedrich Schiller University Jena, Philosophenweg 7a, 07743 Jena, Germany}
\affil[2]{QpiVolta Technologies Pvt Ltd}
\affil[5]{Department of Chemical Engineering \& Biotechnology, University of Cambridge, Philippa Fawcett Drive, Cambridge CB3 0AS, United Kingdom}
\affil[6]{Macromolecular Chemistry, University of Bayreuth, 95447 Bayreuth, Germany}
\affil[\Letter]{\texttt{mail@kjablonka.com}}
\affil[$\star$]{These authors contributed equally.}

>>>>

% Question answerers
\credit{Mehrdad Asgari}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Juliane Eberhardt}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Amir~Mohammad~Elahi}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Christina Glaubitz}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Maximilian Greiner}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Caroline T. Holick}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Tim Hoffmann}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Lea~C.~Klepsch}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Yannik Köster}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Fabian Alexander Kreth}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Jakob~Meyer}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Jan Matthias Peschel}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Michael Ringleb}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Nicole Roesner}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Johanna Schreiber}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Ulrich~S.~Schubert}{0,0,0,1,0,0,0,0,0,0,0,0,0,1}
\credit{Leanne M. Stafast}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}
\credit{Dinga Wonanke}{0,1,0,0,0,0,0,0,0,0,0,0,0,1}

@@

\author[5]{Mehrdad~Asgari~\orcidlink{0000-0002-5427-1610}}
\author[6]{Juliane~Eberhardt~\orcidlink{0009-0000-3991-0704}}
\author[7]{Amir~Mohammad~Elahi~\orcidlink{0009-0001-5907-101X}}
\author[]{Christina~Glaubitz~\orcidlink{0000-0003-3412-0548}}
\author[1]{Maximilian~Greiner}
\author[1]{Caroline~T.~Holick\orcidlink{0009-0000-1724-2725}}
\author[1]{Tim~Hoffmann~\orcidlink{0009-0004-0230-6115}}
\author[1]{Lea~C.~Klepsch~\orcidlink{0009-0009-3849-1670}}
\author[1]{Yannik~Köster~\orcidlink{0000-0002-9125-3067}}
\author[8, 9]{Fabian~Alexander~Kreth~\orcidlink{0000-0002-5968-8706}}
\author[1]{Jakob~Meyer}
\author[10]{Santiago~Miret~\orcidlink{0000-0002-4787-2757}}
\author[1]{Jan~Matthias~Peschel~\orcidlink{0009-0002-4787-2757}}
\author[1]{Michael~Ringleb~\orcidlink{0000-0002-7320-8529}}
\author[1, 11]{Nicole~Roesner~\orcidlink{0000-0002-5133-775X}}

\author[1, 10]{Johanna Schreiber~\orcidlink{0009-0000-0991-8967}}
\author[1,8,11, 12]{Ulrich~S.~Schubert~\orcidlink{0000-0003-4978-4670}}
\author[1, 11]{Leanne~M.~Stafast~\orcidlink{0009-0008-5604-261X}}
\author[13]{Dinga~Wonanke~\orcidlink{0000-0002-9066-2715}}

% Senior authors
\author[14,15]{Michael Pieler~\orcidlink{0000-0001-9186-7045}}
\author[3,4]{Philippe~Schwaller~\orcidlink{0000-0003-3046-6576}}
\author[1,8,11, 12, \Letter]{Kevin~Maik~Jablonka~\orcidlink{0000-0003-4894-4660}}

\affil[1]{Laboratory of Organic and Macromolecular Chemistry (IOMC), Friedrich Schiller University Jena, Humboldtstrasse 10, 07743 Jena, Germany}
\affil[8]{Center for Energy and Environmental Chemistry Jena (CEEC Jena), Friedrich Schiller University Jena, Philosophenweg 7a, 07743 Jena, Germany}
\affil[12]{Helmholtz Institute for Polymers in Energy Applications Jena (HIPOLE Jena), Lessingstrasse 12-14, 07743 Jena, Germany}
\affil[11]{Jena Center for Soft Matter (JCSM), Friedrich Schiller University Jena, Philosophenweg 7, 07743 Jena, Germany}

@@

\affil[7]{Laboratory of Molecular Simulation (LSMO), Institut des Sciences et Ing\'{e}nierie Chimiques, Ecole Polytechnique F\'{e}d\'{e}rale de Lausanne (EPFL), Sion, Switzerland}
\affil[13]{Theoretical Chemistry, Technische Universität Dresden, Dresden 01062, Germany}
\affil[14]{OpenBioML.org}
\affil[15]{Stability.AI}
\affil[9]{Institute for Technical Chemistry and Environmental Chemistry (ITUC), Friedrich Schiller University Jena, Philosophenweg 7a, 07743 Jena, Germany}
\affil[2]{QpiVolta Technologies Pvt Ltd}
\affil[5]{Department of Chemical Engineering \& Biotechnology, University of Cambridge, Philippa Fawcett Drive, Cambridge CB3 0AS, United Kingdom}
\affil[6]{Macromolecular Chemistry, University of Bayreuth, 95447 Bayreuth, Germany}
\affil[10]{Intel Labs}
\affil[\Letter]{\texttt{mail@kjablonka.com}}
\affil[$\star$]{These authors contributed equally.}

### 2024-03-28 src/tex/ms.tex
include tables of dataset sizes

We also gain insight in the struggles the models have with chemical reasoning tasks when we look at the performance as a function of molecular descriptors.
If the model would answer questions based on reasoning about the structures, one would expect the performance to depend on the complexity of the molecules.
We, however, find that the performance of the models does not correlate with complexity indicators but rather trivially with the size of the compounds (see \Cref{fig:performance_per_molecular_size}).
This indicates that the models might not (yet)  be able to reason about the structures of the molecules (in the way one might expect) but rather rely on retrieval of fragments of the training data.
Those observations mirror recent findings that \glspl{llm} struggle to \enquote{reverse} facts they have seen in training (i.e., generalize from \enquote{A has feature B} to \enquote{B is a feature of A}).\autocite{berglund2023reversal, zhu2023physics, allen2023physics, golovneva2024reverse}

@@

\subparagraph{Analytical chemistry}
\variable{output/question_count_per_dir/json_file_counts_analytical_chemistry.txt} questions are based on master student examination papers at the Friedrich Schiller University Jena (Germany). 
These questions focus on the principles and techniques employed in analytical chemistry.

\subparagraph{Combustion engineering}
\variable{output/question_count_per_dir/json_file_counts_combustion_engineering.txt} question is based on a master student examination paper at the University of Magdeburg (Germany). 
It explores topics related to combustion processes and engineering principles.

\subparagraph{Functional materials and nanomaterials}
\variable{output/question_count_per_dir/json_file_counts_func_mats_and_nanomats.txt}  questions are based on exercises in a seminar conducted at the Friedrich Schiller University Jena (Germany), delving into topics concerning functional materials and nanomaterials, exploring their properties and applications.

\subparagraph{General chemistry}
\variable{output/question_count_per_dir/json_file_counts_Gen_Chem_MCA.txt} questions originate from examinations for grade 10 at Marist Comprehensive Academy Uturu (Nigeria). 
They cover fundamental concepts in chemistry suitable for students at the secondary school level.
In addition, we included questions based on the general chemistry courses of the Bachelor of Science in Chemistry at the Technical University of Munich (Germany), focusing on inorganic chemistry (\variable{output/question_count_per_dir/json_file_counts_ac_faessler_tum.txt}) and principles of chemistry (\variable{output/question_count_per_dir/json_file_counts_pum_tum.txt}).

\subparagraph{International Chemical Olympiad}
\variable{output/question_count_per_dir/json_file_counts_icho.txt} questions are based on various countries' Chemical Olympiads, including those held in the USA, UK, and Moldova.

\subparagraph{Material synthesis}
\variable{output/question_count_per_dir/json_file_counts_materials_synthesis.txt} questions are based on seminars on material synthesis at the University of Jena (Germany), focusing on the methods and techniques employed in the synthesis of various materials.

\subparagraph{Organic reactivity}
\variable{output/question_count_per_dir/json_file_counts_organic_reactivity.txt}  questions are primarily sourced from tutorials and exam papers for the Bachelor of Science in Chemistry at the Technical University of Munich (Germany), exploring reactions and mechanisms in organic chemistry.

\subparagraph{Periodic table}
\variable{output/question_count_per_dir/json_file_counts_periodic_table_properties.txt} questions are manually created to cover various aspects and trends of the periodic table.

\subparagraph{Polymer chemistry}
\variable{output/question_count_per_dir/json_file_counts_polymer_chemistry.txt} questions are based on examinations held at the University of Hamburg (Germany), covering topics related to polymer chemistry and its applications.

\subparagraph{Textbook questions}
\variable{output/question_count_per_dir/json_file_counts_oup.txt} questions are based on questions from various textbooks covering biomolecular science, drug synthesis, molecular structure, organic chemistry, and X-ray crystallography.

\subparagraph{Chemical safety} 
This category comprises a total of \variable{output/question_count_per_dir/json_file_counts_safety.txt} questions, including semi-programmatically created questions covering areas such as GHS classification, hazard statements, \gls{dai}, and pictograms from the PubChem database \autocite{pubchem} (see below for details). 
Additionally, it explores crucial topics like materials' compatibility (\variable{output/question_count_per_dir/json_file_counts_materials_compatibility.txt} questions) and chemical compatibility (\variable{output/question_count_per_dir/json_file_counts_chem_chem_comp.txt} questions), essential for understanding the hazardous impact of mixing certain materials and chemicals, via semi-programmatically created questions. 
Furthermore, it includes \variable{output/question_count_per_dir/json_file_counts_blac_gfk.txt} questions based on the question bank published by the Federal/State Working Group on Chemical Safety (BLAC), which is used for the expertise examination (\enquote{Sachkundeprüfung}) according to §11 of the Chemical Prohibition Ordinance (\enquote{Chemikalien-Verbotsverordnung}).\autocite{blac}
Moreover, this category addresses questions about lab safety and topics such as pharmacology, toxicology, material safety data sheets, and chemical safety data sheets. 
The chemical safety category stands out as one of the primary focus areas within the \chembench corpus.

\subparagraph{NMR spectroscopy}
Questions are based on images shared via the Twitter account \url{https://twitter.com/NMRspectroscopy}, focusing on the choice and design of  appropriate \gls{nmr} experiments.

@@

@@

\section*{Data and code availability}
The code and data for \chembench is available at \url{https://github.com/lamalab-org/chem-bench} and archived at \url{XXX}.
The code for the app for our human baseline study is available at \url{https://github.com/lamalab-org/chem-bench-app}. 
To ensure reproducibility, this manuscript was generated using the \href{https://show-your.work/en/latest/}{\\showyourwork} framework.\autocite{Luger2021}
The code to rebuild the paper (including code for all figures and numbers next to which there is a GitHub icon) can be found at \url{\GitHubURL}. 
To facilitate reproduction, some intermediate results of the analysis are cached at \url{http://dx.doi.org/10.5072/zenodo.34706 }.

\section*{Acknowledgements}
This work was supported by the Carl Zeiss Foundation, a \enquote{Talent Fund} of the \enquote{Life} profile line of the Friedrich Schiller University Jena and the FAIRmat consortium.
We also thank Stability.AI for the use of its HPC cluster and for its generous donations.
In addition, we thank the OpenBioML.org community and their ChemNLP project team for useful discussions.
Moreover, we thank Pepe Márquez, and Santiago Miret for discussion and support and Julian Kimmig for feedback on the web app.

>>>>

We also gain insight in the struggles the models have with chemical reasoning tasks when we look at the performance as a function of molecular descriptors.
If the model would answer questions based on reasoning about the structures, one would expect the performance to depend on the complexity of the molecules.
We, however, find that the performance of the models does not correlate with complexity indicators but rather trivially with the size of the compounds (see XX).
This indicates that the models might not (yet)  be able to reason about the structures of the molecules (in the way one might expect) but rather rely on retrieval of fragments of the training data.
Those observations mirror recent findings that \glspl{llm} struggle to \enquote{reverse} facts they have seen in training (i.e., generalize from \enquote{A has feature B} to \enquote{B is a feature of A}).\autocite{berglund2023reversal, zhu2023physics, allen2023physics, golovneva2024reverse}

@@

\input{sections/manually_sources_table.tex}

@@

\input{sections/semi_programatically_sources_table.tex}

@@

\section*{Data and code availability}
The code and data for \chembench is available at \url{https://github.com/lamalab-org/chem-bench}.
The code for the app for our human baseline study is available at \url{https://github.com/lamalab-org/chem-bench-app}. 
To ensure reproducibility, this manuscript was generated using the \href{https://show-your.work/en/latest/}{\\showyourwork} framework.\autocite{Luger2021}
The code to rebuild the paper (including code for all figures and numbers next to which there is a GitHub icon) can be found at \url{\GitHubURL}. 
To facilitate reproduction, some intermediate results of the analysis are cached at \url{http://dx.doi.org/10.5072/zenodo.34706}.

\section*{Acknowledgements}
This work was supported by the Carl Zeiss Foundation, a \enquote{Talent Fund} of the \enquote{Life} profile line of the Friedrich Schiller University Jena and the FAIRmat consortium.
We also thank Stability.AI for the use of its HPC cluster and for its generous donations.
In addition, we thank the OpenBioML.org community and their ChemNLP project team for useful discussions.
Moreover, we thank Pepe Márquez for discussion and support and Julian Kimmig for feedback on the web app.

### 2024-03-28 src/tex/sections/manually_sources_table.tex
include tables of dataset sizes

\hline
NMR spectroscopy & Questions are based on images shared via the Twitter account (https://twitter.com/NMRspectroscopy). & 5 \\
\hline
Analytical chemistry & Questions are based on exercises in master student examination at the Friedrich Schiller University, Jena, Germany. & 22 \\
\hline
\multirow{2}{*}{General chemistry} & Questions originate from examinations for grade 10 at the Marist Comprenhensive Academy Uturu, Nigeria. & 6 \\
 & Questions originate from the Bachelor of Science courses  at the Technical University of Munich, Germany. & 8 \\
 \hline
\begin{tabular}[c]{@{}l@{}}Functional materials and \\ nanomaterials\end{tabular} & Questions are based on exercises in a seminar conducted at the Friedrich Schiller University, Jena, Germany. & 8 \\
\hline
Combustion engineering & Based on a Master of Science examination paper at the University of Magdeburg, Germany & 1 \\
\hline
Materials' synthesis & Questions are based on seminars on material synthesis from Friedrich Schiller University, Jena, Germany. & 11 \\

\hline
Chemistry olympiad & National and International Olympiads held in US, UK and Moldova & 193 \\
Organic reactivity & Based on Bachelor of Science in Chemistry at the Technical University of Munich, Germany & 34 \\
\hline
Periodic table & Manually created & 15 \\
\hline
Polymer chemistry & Based on examinations at the University of Hamburg, Germany & 17 \\
\hline
Textbook questions & Various textbooks covering biomolecular science, drug synthesis, molecular structure, organic chemistry, and X-ray crystallography. & 202 \\
\hline
\multirow{1}{*}{Safety} &
 Based on the question bank published by the Federal/State Working Group  on Chemical Safety (BLAC), which is used for the expertise examination (“Sachkundeprufung”) & 90 \\
\hline
\end{tabular}
\end{table}

>>>>

\begin{table}[h]
    \begin{tabularx}{\textwidth}{Xp{7 cm}X}
    \toprule
    source & description & question count \\
    \midrule
NMR spectroscopy & Questions are based on images shared via the Twitter account (https://twitter.com/NMRspectroscopy). & 5 \\
\
Analytical chemistry & Questions are based on exercises in master student examination at the Friedrich Schiller University, Jena, Germany. &  \variable{output/question_count_per_dir/json_file_counts_analytical_chemistry.txt} \\
\
\multirow{2}{*}{General chemistry} & Questions originate from examinations for grade 10 at the Marist Comprenhensive Academy Uturu, Nigeria. & \variable{output/question_count_per_dir/json_file_counts_Gen_Chem_MCA.txt} \\
 & Questions originate from the Bachelor of Science (for chemistry) courses at the Technical University of Munich, Germany. & 8 \\
Functional materials and  nanomaterials & Questions are based on exercises in a seminar conducted at the Friedrich Schiller University, Jena, Germany. & \variable{output/question_count_per_dir/json_file_counts_func_mats_and_nanomats.txt} \\
Combustion engineering & Based on a Master of Science examination paper at the University of Magdeburg, Germany & \variable{output/question_count_per_dir/json_file_counts_combustion_engineering.txt} \\
Materials' synthesis & Questions are based on seminars on material synthesis from Friedrich Schiller University, Jena, Germany. & \variable{output/question_count_per_dir/json_file_counts_materials_synthesis.txt} \\
Chemistry olympiad & National and International Olympiads held in US, UK and Moldova & \variable{output/question_count_per_dir/json_file_counts_icho.txt} \\
Organic reactivity & Based on Bachelor of Science in Chemistry at the Technical University of Munich, Germany & \variable{output/question_count_per_dir/json_file_counts_organic_reactivity.txt} \\
Periodic table & Manually created & \variable{output/question_count_per_dir/json_file_counts_periodic_table_properties.txt} \\
Polymer chemistry & Based on examinations at the University of Hamburg, Germany & \variable{output/question_count_per_dir/json_file_counts_polymer_chemistry.txt} \\
Textbook questions & Various textbooks covering biomolecular science, drug synthesis, molecular structure, organic chemistry, and X-ray crystallography. & \variable{output/question_count_per_dir/json_file_counts_oup.txt} \\
Safety & Based on the question bank published by the Federal/State Working Group  on Chemical Safety (BLAC), which is used for the expertise examination (“Sachkundeprufung”) & \variable{output/question_count_per_dir/json_file_counts_blac_gfk.txt} \\
\bottomrule
\end{tabularx}
\end{table}

### 2024-03-28 src/tex/sections/semi_programatically_sources_table.tex
Update src/tex/sections/semi_programatically_sources_table.tex
include tables of dataset sizes

\begin{table}[h]
\begin{tabular}{lp{7 cm}r}
\hline
\textbf{Subset} & \textbf{Source description} & \textbf{\#} \\
\hline
Number of isomers & MAYGEN was used to compute the number of isomers for a set of SMILES extracted from the ZINC dataset. & \variable{output/question_count_per_dir/json_file_counts_number_of_isomers.txt} \\
\hline
\begin{tabular}[c]{@{}l@{}}Total electron count of \\ molecules\end{tabular} & Electron counts based on the data from https://www.cheminfo.org/. & \variable{output/question_count_per_dir/json_file_counts_electron_counts.txt} \\
\hline
Oxidation states & Oxidation states questions based on the data from https://www.cheminfo.org/. & \variable{output/question_count_per_dir/json_file_counts_oxidation_states.txt} \\
\hline
Chemical reactivity & Questions are framed based on the information from Cameo Chemicals website (https://cameochemicals.noaa.gov/reactivity). & \variable{output/question_count_per_dir/json_file_counts_reactive_groups.txt} \\
\hline
Number of NMR peaks & Molecules are sampled from the ZINC database and the number of NMR peaks is computed with OpenChemLib & \variable{output/question_count_per_dir/json_file_counts_number_of_nmr_peaks.txt} \\
\hline
Point group of molecules & Our ChemCaption tool is used to assign the point group, and then each case was manually checked to select well defined cases. & \variable{output/question_count_per_dir/json_file_counts_point_group.txt} \\
IUPAC-SMILES pairs & Sampled from the PubChem database & \variable{output/question_count_per_dir/json_file_counts_smiles_to_name.txt} + \variable{output/question_count_per_dir/json_file_counts_smiles_to_name.txt} \\
\hline
\multirow{3}{*}{PubChem safety data} & Daily allowable intakes according to the World Health Organization & \variable{output/question_count_per_dir/json_file_counts_dai.txt}  \\
 & Definitions of hazard statements &  \variable{output/question_count_per_dir/json_file_counts_h_statements.txt} \\
 & GHS classification of chemicals mined through the API & \variable{output/question_count_per_dir/json_file_counts_pictograms.txt} \\
\hline
\multirow{2}{*}{Safety}
& Materials' compatibility & \variable{output/question_count_per_dir/json_file_counts_materials_compatibility.txt} \\
 & Chemical compatibility & \variable{output/question_count_per_dir/json_file_counts_chem_chem_comp.txt} \\
\hline
\end{tabular}
\end{table}

>>>>

\begin{table}[h]
\begin{tabularx}{\textwidth}{Xp{7 cm}X}
    \toprule
    source & description & question count \\
\midrule
Number of isomers & MAYGEN was used to compute the number of isomers for a set of SMILES extracted from the ZINC dataset. & \variable{output/question_count_per_dir/json_file_counts_number_of_isomers.txt} \\
Total electron count of molecules & Electron counts based on the data from https://www.cheminfo.org/. & \variable{output/question_count_per_dir/json_file_counts_electron_counts.txt} \\
Oxidation states & Oxidation states questions based on the data from https://www.cheminfo.org/. & \variable{output/question_count_per_dir/json_file_counts_oxidation_states.txt} \\
Chemical reactivity & Questions are framed based on the information from Cameo Chemicals website (https://cameochemicals.noaa.gov/reactivity). & \variable{output/question_count_per_dir/json_file_counts_reactive_groups.txt} \\
Number of NMR signals & Molecules are sampled from the ZINC database and the number of NMR signals is computed with OpenChemLib & \variable{output/question_count_per_dir/json_file_counts_number_of_nmr_peaks.txt} \\
Point group of molecules & Our ChemCaption tool is used to assign the point group, and then each case was manually checked to select well defined cases. & \variable{output/question_count_per_dir/json_file_counts_point_group.txt} \\
IUPAC-SMILES pairs & Sampled from the PubChem database & \variable{output/question_count_per_dir/json_file_counts_smiles_to_name.txt} + \variable{output/question_count_per_dir/json_file_counts_smiles_to_name.txt} \\
\multirow{3}{*}{PubChem safety data} & Daily allowable intakes according to the World Health Organization & \variable{output/question_count_per_dir/json_file_counts_dai.txt}  \\
 & Definitions of hazard statements &  \variable{output/question_count_per_dir/json_file_counts_h_statements.txt} \\
 & GHS classification of chemicals mined through the API & \variable{output/question_count_per_dir/json_file_counts_pictograms.txt} \\
\multirow{2}{*}{Safety}
& Materials' compatibility & \variable{output/question_count_per_dir/json_file_counts_materials_compatibility.txt} \\
 & Chemical compatibility & \variable{output/question_count_per_dir/json_file_counts_chem_chem_comp.txt} \\
\bottomrule
\end{tabularx}
\end{table}
